Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-02 astronum_2019_MAESTROeX/astronum-maestroex.tex
updated GPU plot to include speedups

\begin{figure}\label{fig:gpu_speedup}
    \centering

@@

    \caption{Comparison of the performance of functions on the CPU vs the GPU. The plot shows the average execution time for several functions, recorded for a run of the 3d \texttt{reacting\_bubble} problem on Summit. Both tests were performed using a single node, with the CPU test using 42 MPI processes, each with 4 OpenMP threads, and the GPU test using 6 MPI processes, each process associated with a single GPU. Note that the $x$-axis scale is logarithmic.}

@@

\ack Visualizations were probably done using~\cite{yt}.

% The work at Stony Brook was supported by DOE/Office of Nuclear
% Physics grant DE-FG02-87ER40317 and contract 7418390 with Lawrence
% Berkeley National Laboratory as part of the Exascale Compute Project
% ExaStar collaboration.  The work at LBNL was supported by the DOE
% Office of Advanced Scientific Computing Research under Contract No,
% DE-AC02-05CH11231. An award of computer
% time was provided by the Innovative and Novel Computational Impact on
% Theory and Experiment (INCITE) program. This research used resources
% of the Oak Ridge Leadership Computing Facility at the Oak Ridge
% National Laboratory, which is supported by the Office of Science of
% the U.S. Department of Energy under Contract No.\ DE-AC05-00OR22725.
% This research used resources of the National Energy Research
% Scientific Computing Center, which is supported by the Office of
% Science of the U.S. Department of Energy under Contract
% No.\ DE-AC02-05CH11231.  Visualizations were done using yt~\cite{yt}.
% This research has made use of NASA's Astrophysics Data System
% Bibliographic Services.

>>>>

\begin{figure}
    \centering

@@

    \caption{Comparison of the performance of functions on the CPU vs the GPU. The plot shows the average execution time for several functions, recorded for a run of the 3d \texttt{reacting\_bubble} problem on Summit. Both tests were performed using a single node, with the CPU test using 42 MPI processes, each with 4 OpenMP threads, and the GPU test using 6 MPI processes, each process associated with a single GPU. Note that the $x$-axis scale is logarithmic.}\label{fig:gpu_speedup}

@@

\ack Figure~\ref{fig:gpu_speedup} was generated using \texttt{Jupyter} \citep{Kluyver2016} and \texttt{matplotlib} \citep{Hunter2007}.

% The work at Stony Brook was supported by DOE/Office of Nuclear
% Physics grant DE-FG02-87ER40317 and contract 7418390 with Lawrence
% Berkeley National Laboratory as part of the Exascale Compute Project
% ExaStar collaboration.  The work at LBNL was supported by the DOE
% Office of Advanced Scientific Computing Research under Contract No,
% DE-AC02-05CH11231. An award of computer
% time was provided by the Innovative and Novel Computational Impact on
% Theory and Experiment (INCITE) program. This research used resources
% of the Oak Ridge Leadership Computing Facility at the Oak Ridge
% National Laboratory, which is supported by the Office of Science of
% the U.S. Department of Energy under Contract No.\ DE-AC05-00OR22725.
% This research used resources of the National Energy Research
% Scientific Computing Center, which is supported by the Office of
% Science of the U.S. Department of Energy under Contract
% No.\ DE-AC02-05CH11231.
